\large{Vipassana for Hackers} \\ \Huge{Paper Two: The Brain} \\ \large\textit{Version 0.2}

### 2019-10-07 paper-two/paper-two.tex
completed todo -1 : added information about ipl with 2 references

The Inferior Parietal lobe (IPL) is situated in the back of the brain and it is
involved in the perception of facial stimuli. \cite{ipl}

\todo{Expand on IPL: How does the IPL contribute to our sense of self?}

@@

>>>>

The Inferior Parietal lobe (IPL) is situated in the back of the brain and it is
involved in the perception of facial stimuli. \cite{ipl}.In a study previously conducted where
subjects were asked to retrieve previous judgments about oneself, their friend and the Dutch queen, 
the activation of the IPL decreased with decreasing self reference. \cite{iplself} 
Another study used Transcranial Magnetic Stimulation (TMS) to create a sort of virtual lesion of
the right-IPL and showed that this disrupts self-other discrimination. \cite{ipltms}

@@

\bibitem{iplself}
 Hans C. Lou, Bruce Luber, Michael Crupain, Julian P. Keenan, Markus Nowak, 
 Troels W. Kjaer, Harold A. Sackeim, Sarah H. Lisanby
 \textit{Parietal cortex and representation of the mental Self}
  Proc Natl Acad Sci U S A. 2004 Apr 27; 101(17): 6827–6832.

\bibitem{ipltms}
 Lucina Q. Uddin, Istvan Molnar-Szakacs, Eran Zaidel, Marco Iacoboni
 \textit {rTMS to the right inferior parietal lobule disrupts self–other discrimination}
  Social Cognitive and Affective Neuroscience, Volume 1, Issue 1, June 2006, 
  Pages 65–71, https://doi.org/10.1093/scan/nsl003
